Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-16 docs/undergraduate-research-symposium-images.qmd
simplify project structure

   p <- ggplot(d, aes(x, y)) +
     geom_tile(col = "grey50", 
               linewidth = 0.5, 
               aes(fill = ifelse(z == 1, palette_colors, "white"))) +
     scale_fill_identity() +  
     coord_equal(expand = FALSE) +
     scale_x_continuous(
       breaks = 1:ncol(x),
       labels = col_labels,
       position = "top"
     ) +
     scale_y_continuous(
       breaks = 1:nrow(x),
       labels = row_labels
     ) +
     theme(
       axis.text = element_text(size = rel(0.3)),
       axis.ticks = element_blank(),
       legend.position = "none",
       plot.title = element_text(hjust = 1)
     ) +
     labs(x = "", y = "") +
     rotate_x_text(angle = 90, hjust = 0, vjust = 0.5)

@@

   final_plot <- ggraph(disim_net, layout="fr") +
       geom_edge_link(aes(width = weight, 
                          alpha=weight), 
                      edge_colour = "black", 
                      show.legend= F,
                     ) +
       scale_edge_width(range=c(0.5,1.5)) +
       scale_edge_colour_gradient(low = "#CCCCCC",
                                  high = "#000000") +
       geom_node_point(alpha=1, size=5) +
       geom_node_text(aes(label=row.names(artifact_data)), 
                      size=3, 
                      family= "Arial", 
                      repel=T, max.overlaps = 100) +
       theme(text= element_text(size = 15), 
             panel.background = element_rect(fill = 'white')) +
     border(color = "black", size = 0.5)

@@

```{r}
ser_net_trans <- plot_grid(seriation_trans, network_trans, align = "hv", labels = "AUTO", rel_widths = c(1.3, 1.4))
ser_net_proto <- plot_grid(seriation_proto, network_proto, align = "hv", rel_widths = c(1.4, 1.4))
ser_net_early <- plot_grid(seriation_early, network_early, align = "hv", rel_widths = c(1.65, 1.8))
ser_net_evo <- plot_grid(seriation_evolved, network_evolved, align = "hv", rel_widths = c(1.4, 1.4))

final <- plot_grid(ser_net_trans, ser_net_proto, ser_net_early, ser_net_evo, align = "hv", ncol = 1, labels = c("Transitional", "Proto", "Early", "Evolved"))

ggsave(final, 
      filename =  "poster.png",
       bg = "white", h = 9, w = 4.5)
```

```{r}
ser_net_trans <- plot_grid(seriation_trans, network_trans, align = "hv", labels = "AUTO", ncol = 1)
ser_net_proto <- plot_grid(seriation_proto, network_proto, align = "hv", ncol = 1)
ser_net_early <- plot_grid(seriation_early, network_early, align = "hv", ncol = 1)
ser_net_evo <- plot_grid(seriation_evolved, network_evolved, align = "hv", ncol = 1)

final <- plot_grid(ser_net_trans, ser_net_proto, ser_net_early, ser_net_evo, align = "hv", ncol = 4, labels = c("Transitional", "Proto", "Early", "Evolved"))

ggsave(final, 
      filename =  "poster2.png",
       bg = "white", w = 12)

@@

```{r}
ser_plot <- plot_grid(seriation_trans, seriation_proto, seriation_early, seriation_early, align = "hv", ncol = 1, labels = c("Transitional", "Proto", "Early", "Evolved"), label_size = 9)
net_plot <- plot_grid(network_trans, network_proto, network_early, network_evolved, align = "hv", ncol = 1)

  final <- plot_grid(ser_plot, net_plot, align = "hv", ncol = 2, rel_widths = c(1.3, 1), labels = "AUTO", label_x = c(0, -0.07))

ggsave(final, 
      filename =  "poster3.png", bg = "white", w = 5, h = 7)
```

@@

sign_type_plot <- ggplot(sign_type_df) +
  aes(reorder(sign_type, value), x = sign_type, y = value) +
  geom_col() +
  xlab("Sign type") +
  ylab("Count") +
  theme(axis.title = element_text(size = 10)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, ))

ggsave(sign_type_plot, 
      filename =  "signtype.png",
       bg = "white", w = 5, h = 3)

>>>>

   p <- ggplot(d, aes(x, y)) +
     geom_tile(col = "grey50", 
               linewidth = 0.5, 
               aes(fill = ifelse(z == 1, palette_colors, "white"))) +
     scale_fill_identity() +  
     coord_equal(expand = FALSE) +
     scale_x_continuous(
       breaks = 1:ncol(x),
       labels = col_labels,
       position = "top"
     ) +
     scale_y_continuous(
       breaks = 1:nrow(x),
       labels = row_labels
     ) +
     theme(
       axis.text = element_text(size = rel(0.5)),
       axis.ticks = element_blank(),
       legend.position = "none",
       plot.title = element_text(hjust = 1)
     ) +
     labs(x = "", y = "") +
     rotate_x_text(angle = 90, hjust = 0, vjust = 0.5)

@@

   final_plot <- ggraph(disim_net, layout="fr") +
       geom_edge_link(aes(width = weight, 
                          alpha=weight), 
                      edge_colour = "grey50", 
                      show.legend= F,
                     ) +
       scale_edge_width(range=c(0.5,1.5)) +
       scale_edge_colour_gradient(low = "grey80",
                                  high = "grey50") +
       geom_node_point(alpha=1, size=5, colour = "grey60") +
       geom_node_text(aes(label=row.names(artifact_data)), 
                      size=2, 
                      family= "Arial", 
                      repel=T, max.overlaps = 100) +
       theme(text= element_text(size = 15), 
             panel.background = element_rect(fill = 'white')) +
     border(color = "black", size = 0.5)

@@

```{r}
# BM: I think it might be easier to align if there are two separate columns of plots
# top, right, bottom, left

ser_plot <- plot_grid(seriation_trans + theme(plot.margin =   unit(c( 0, 0, -10, 0), "cm")),
                      seriation_proto + theme(plot.margin =   unit(c(-10, 0, -10, 0), "cm")), 
                      seriation_early + theme(plot.margin =   unit(c(-10, 0, -10, 0), "cm")), 
                      seriation_evolved + theme(plot.margin = unit(c(-10, 0,  0, 0), "cm")),
                      align = "hv", 
                      ncol = 1, 
                      labels = c( 
                                 "Transitional",   
                                 "Proto",  
                                 "Early",  
                                 "Evolved"), 
                      label_size = 9, 
                      label_x = rep(0.35, 4), 
                      hjust = 1, 
                      label_y = rep(0.7, 4))

ggsave(ser_plot, 
      filename =  here::here("Extra/poster4-seriation.png"), 
      bg = "white", 
      w = 4.5, 
      h = 8)

net_plot <- plot_grid(network_trans, NULL,
                      network_proto, NULL,
                      network_early, NULL,
                      network_evolved, NULL,
                      rel_heights = c(1, 0.1, 1, 0.1, 1, 0.1, 1, 0.1),
                      align = "hv", 
                      ncol = 1)

ggsave(net_plot, 
      filename =  here::here("Extra/poster4-networks.png"), 
      bg = "white", 
      w = 3, 
      h = 8)

@@

@@

sign_type_plot <- ggplot(sign_type_df) +
  aes(x = reorder(sign_type, -value), y = value) +
  geom_col() +
  xlab("") +
  ylab("Count") +
  theme_minimal(base_size = 12) +
  theme(axis.title = element_text(size = 10)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(sign_type_plot, 
      filename =  here::here("Extra/signtype.png"),
       bg = "white", w = 5, h = 7)
